On X-ray emission from Fast Blue Optical Transients

### 2023-05-11 papers/FBOTcompton/fbotcompton.tex
paper

Let consider different models of origin of X-ray radiation, which observed flux in energy range $0.3 - 10\text{ }keV$ is $(1.33 \pm 0.76) \times 10^{-15}\text{ }erg\text{ }s^{-1} cm^{-2}$.. At first, we assume that it is synchrotron radiation from the electron distribution, which is prolonged to much higher energies than it is possible to reach in PIC simulation. The necessary energy of electrons is determined by energy of emitted photon $E_e = (4\pi{m_e}^3 c^5 E_{ph}/0.29\cdot3 e B h)^{1/2} \approx 2\cdot10^6 m_e c^2$. The flux from source with parameters obtained in section \ref{synchrotron} and prolonged distribution is $what$. But on should take into account tht lifeime of electrons with this energy in magnetic field $B \approx 0.6 G$ is $\tau = {m_e}^4 c^7 / e^4 B^2 E_e \approx 10^3 s$ and distance that electron can move on this time is about $d = 3\cdot10^13 cm$. This means that emitting volume drasticaly decreases and we should evaluate radiation of spherical layer with width $d$.

>>>>

Let consider different models of origin of X-ray radiation, which observed flux in energy range $0.3 - 10\text{ }keV$ is $(1.33 \pm 0.76) \times 10^{-15}\text{ }erg\text{ }s^{-1} cm^{-2}$.

At first, we assume that it is synchrotron radiation from the electron distribution, which is prolonged to much higher energies than it is possible to reach in PIC simulation. The necessary energy of electrons is determined by energy of emitted photon $E_e = (4\pi{m_e}^3 c^5 E_{ph}/0.29\cdot3 e B h)^{1/2} \approx 2\cdot10^6 m_e c^2$. The flux from source with parameters obtained in section \ref{synchrotron} and prolonged distribution is $what$. But on should take into account tht lifeime of electrons with this energy in magnetic field $B \approx 0.6 G$ is $\tau = {m_e}^4 c^7 / e^4 B^2 E_e \approx 10^3 s$ and distance that electron can move on this time is about $d = 3\cdot10^13 cm$. This means that emitting volume drasticaly decreases and we should evaluate radiation of spherical layer with width $d$, and the resulting synchrotron X-ray flux is $what$.

Another option of X-ray source is inverse compton scattering of electrons in the ejecta on photons from the star.
